Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-06-25 paper2.qmd
review and editing

>>>>

# Conclussion {#sec-conclussion}

This paper underscores the need to extend Thurstone's theory to meet the demands of contemporary empirical CJ research. It specifically advocates for the development of bespoke CJ models aligned with the underlying data-generating processes of specific CJ assessment designs, as these models have the potential to strengthen the robustness of trait estimates and the clarity of inferences. The work also outlines a clear trajectory for advancing CJ research in both theoretical and applied domains. Finally, the study also lays the groundwork for broader applications, encouraging researchers across the social sciences to adopt more robust and interpretable methodologies.
